\section{Conceptual Framework}

The paper separates three concepts that are often conflated. Fuel poverty identifies present affordability hardship under current prices and required energy needs. Energy burden measures required or actual energy cost relative to residual household income. Household fuel price risk captures future exposure, sensitivity, and limited adaptive capacity under price-shock scenarios. The first is a condition, the second is a ratio, and the third is a forward-looking risk relation.
% Citation TODO: official fuel poverty measurement, energy burden literature, energy vulnerability literature.

\begin{equation}
\text{Household fuel price risk} = \text{exposure} + \text{sensitivity} - \text{adaptive capacity}.
\end{equation}

This expression is a conceptual guide rather than a claim that risk is literally additive in all empirical settings. Its purpose is to keep the three causal channels visible. Exposure refers to the household's dependence on fuels, tariffs, standing charges, and required energy demand that are vulnerable to price shocks. Sensitivity refers to how strongly a price change affects household welfare, largely through residual income, required energy services, health needs, household composition, and debt or arrears. Adaptive capacity refers to the household's ability to avoid, absorb, or reduce the shock through savings, tariff switching, demand flexibility, fabric improvement, heating-system change, PV or storage access, public support, landlord action, or building-level governance.

This distinction matters because the same observed energy bill can imply different risks. A low bill may indicate an efficient dwelling, but it may also indicate underheating or self-rationing. A high required energy cost may be manageable for a high-income household, but destabilising for a household with low after-housing-cost income. A low-carbon heating system may reduce direct gas exposure, but it can increase sensitivity to electricity prices if the dwelling remains inefficient or if the household cannot access an appropriate tariff. Household fuel price risk therefore cannot be read from EPC rating, current expenditure, or technology adoption alone.

The implemented baseline burden indicators should therefore be read as current-price affordability measures, not as the final fuel-price-risk outcome. They provide the income--cost foundation for later shock scenarios, but they do not themselves represent future exposure unless fuel-price, tariff, and intervention counterfactuals are introduced.

In the empirical work, this distinction is operationalised through two related but non-equivalent burden measures. The first is a deterministic baseline required-energy-burden ratio: SAP-derived required energy cost divided by MSOA after-housing-cost disposable income. The second is a probabilistic threshold measure: the probability that a household drawn from the property's LSOA income distribution would face a required energy burden above 10 percent. The former is intuitive as a cost-to-income ratio; the latter is better suited to identifying local income-tail exposure. Neither measure is an official fuel-poverty classification, and neither should be read as future household fuel price risk before price shocks are modelled.

The use of required energy costs is central to the concept. Required demand asks what a household would need to spend to secure adequate domestic energy services, rather than what it actually spends after coping strategies have already occurred. This is analytically preferable where high prices may lead households to reduce heating, hot water, cooking, lighting, or appliance use below acceptable levels. A risk framework based only on actual expenditure would risk misclassifying households that appear inexpensive because they are already sacrificing comfort or welfare.
% Citation TODO: required versus actual energy use, prebound/underconsumption, hidden energy poverty.

The probabilistic burden measure is also conceptually necessary. Westminster's property records do not reveal the income of the current occupant, and a single MSOA income point estimate would hide lower-tail households living within otherwise affluent areas. Drawing from constrained LSOA income distributions does not claim to observe each household. Instead, it estimates how likely a property with a given required cost would become high-burden if occupied by households drawn from the local residual-income distribution. This is why the model reports both deterministic burden intensity and probabilistic threshold exposure.

This matters for interpretation. A top-decile modelled burden-risk group identifies the high end of Westminster's current required-cost and income-distribution assumptions. It does not mean that every property in that group is occupied by a verified fuel-poor household, nor that all other properties are protected. Instead, it marks where required energy demand, local income sensitivity, and dwelling characteristics make high burden more probable under current prices. The future-facing risk analysis must then ask how this baseline exposure changes when gas prices, electricity prices, standing charges, tariff access, and policy mitigations are varied.

The conceptual framework also clarifies how domestic net zero interventions should be interpreted. Fabric retrofit primarily de-risks by lowering required heat demand, which reduces exposure to any future unit price. Clean heat primarily changes the fuel vector and system efficiency; its risk effect depends on the electricity-gas price ratio, seasonal performance, fabric condition, and tariff access. PV and batteries hedge electricity-price exposure only where roof rights, dwelling form, tenure, capital access, storage economics, and export or time-of-use tariffs permit the household to capture the benefit. Smart tariffs and flexibility can reduce costs for households able to shift demand, but can also reproduce inequality where digital access, smart-meter access, automation, or load flexibility are uneven. Bill support, standing-charge reform, and social tariffs reduce sensitivity directly, but do not necessarily reduce physical exposure.
% Citation TODO: retrofit, heat pump, PV/battery, smart tariff and bill equity evidence.

This is why decarbonisation is not the same as de-risking. Electrification can reduce emissions before it reduces household price risk where electricity prices remain linked to gas through wholesale market design or where electricity remains expensive relative to gas at the retail level. Conversely, an intervention that is modest in carbon terms may still be protective if it reduces upper-tail burden risk for households with little adaptive capacity. The protective value of heat pumps, PV, storage, smart tariffs, and flexibility therefore depends on the electricity-gas price ratio, tariff access, capital access, dwelling form, tenure, and governance.

The framework implies a specific empirical test. A satisfactory model must identify baseline required-cost exposure, represent income sensitivity without pretending to know each occupant's income, expose households to fuel-price and tariff scenarios, and then estimate whether intervention packages reduce upper-tail burden risk after feasibility constraints are applied. This is why the paper uses burden ratios, threshold-crossing probabilities, expected shortfall-style affordability gaps, Fuel Price-at-Risk, and de-risking dividends. Together, these measures are sufficient for the paper's purpose because they answer the distributional question directly: not whether an intervention improves the average dwelling, but whether it reduces the probability and severity of unaffordable required energy costs for the households and dwelling types most exposed to shocks.
