\section{Case and Data}

The empirical case is Westminster, London. The preferred unit of analysis is the property or household-dwelling pair. Where household microdata are unavailable, the study uses EPC property records combined with LSOA/MSOA income and deprivation proxies to assign synthetic households or archetypes.

Westminster is not treated as a generic affluent borough. Its relevance lies in the coexistence of high aggregate wealth with residual-income pressure, older and heterogeneous housing, private renting, leasehold flats, conservation and heritage constraints, and social housing retrofit pathways. These features are not background descriptors; they shape exposure, sensitivity, and adaptive capacity. In a high-cost city, households can face fuel-price vulnerability through the combination of required heat demand and constrained residual income even where area-level averages appear comfortable.

The current enriched property master contains 124,980 properties across 126 LSOAs and 26 MSOAs. It combines EPC attributes, spatial identifiers, MSOA after-housing-cost income, LSOA income deprivation, official LSOA fuel poverty rates, and LSOA income-distribution outputs from the latest verified pipeline.

The 2026-05-28 baseline modelling extract fixes this backbone into a 77-column, shock-ready input layer. It should be interpreted as a baseline required-burden dataset, not as a completed household fuel price risk model. The extract preserves the 124,980 Westminster property records, passes 22 QA checks with no warnings or failures, and records the fields needed to join property characteristics, LSOA income distributions, main fuel, payment-method sensitivity labels, and future price-spine scenarios. This boundary is important because the extract locks the current required-cost denominator and numerator before any fuel-price shock, mitigation scenario, or intervention counterfactual is applied.

The spatial outputs use the 123 Westminster LSOAs available in the current GIS boundary file. The three data LSOAs without matching polygons, containing 44 properties, are retained in all non-spatial analysis but omitted from the map panels. This boundary should be kept explicit when interpreting the spatial concentration results in Figure~\ref{fig:spatial-high-risk}.

The latest EPC enrichment step links certificate records to the Westminster property master by UPRN, applies consistent UPRN normalisation in both merge and QA stages, and retains one selected EPC certificate per property using the latest lodgement or inspection date. The audited enriched stock preserves the master row count and reports zero unmatched master rows after the corrected linkage. EPC-derived tenure is used only as a proxy for tenure-related governance and adaptive capacity; the corrected analysis version classifies the stock as 58,744 private rented properties, 43,686 owner-occupied properties, 20,066 social rented properties, and 2,484 unknown-tenure properties.

The analysis uses required energy demand rather than only observed expenditure, because actual consumption may understate unmet need through underheating or self-rationing.

The newly imported official price-spine materials extend this backbone by adding the retail-facing price input layer required for future shock analysis. The spine is built for the Ofgem London region and preserves payment method, fuel, unit rate, daily standing charge, VAT treatment, scenario window, source provenance, and region-basis flags. It should be understood as the external price-shock and retail pass-through layer, not as a household bill result by itself. The household fuel price risk estimates will only emerge after this price layer is joined to required energy demand, residual income, dwelling-fuel characteristics, and intervention feasibility.
% Source TODO: cite Ofgem default tariff cap levels, Ofgem unit rates and standing charges, GOV.UK Energy Price Guarantee regional rates, and DESNZ petroleum product monthly statistics.

The domestic modelling spine contains scenarios S0--S6. S0 establishes the April--September 2021 pre-shock reference period; S1 and S2 capture successive post-COVID and pre-Ukraine tariff-cap uplifts; S3 represents unmitigated 2022Q4 Ofgem cap exposure; S4 keeps the Energy Price Guarantee observed 2022Q4 unit-rate support analytically separate from S3; S5 covers heating-oil exposure for off-gas or oil-heated dwellings; and S6 is a 2026 fixed-cost and standing-charge sensitivity. Road fuel is retained only as an optional appendix input and is not part of the core domestic heating and electricity model. This design is important because it keeps regulated mains energy, unregulated off-gas fuels, policy mitigation, and fixed-cost tariff structure in separate mechanisms.

The new price-structure sensitivity archive adds a robustness layer to this data logic. It compares the SAP-inverse required-cost measure used in the baseline model with EPC certificate heating, hot water, and lighting component costs, and with an exploratory unit-rate versus standing-charge decomposition. This archive uses the same 124,980-row Westminster property backbone and preserves the master row count, but it should not be treated as a replacement for the canonical baseline model. The EPC component total excludes cooking because the matched EPC certificate fields do not provide a separate cooking-cost variable; the unit-plus-standing measure also equals the EPC component total by construction. The archive is therefore used to test whether burden rankings are sensitive to cost definition and price structure, not to provide an official fuel-poverty measure or a full future price-shock engine.

The baseline extract now makes this distinction operational. The main baseline metric is \texttt{sap\_inverse\_total\_cost}, equal to the SAP-inverse modelled required energy cost. The price-revaluable bridge is \texttt{epc\_component\_total\_cost}, defined as EPC heating, hot-water, and lighting cost. The former is used for baseline burden ranking and high-burden group flags; the latter is retained for downstream repricing because it can be decomposed into service-component costs. Payment method is not observed at household level and is therefore stored only as scenario metadata for Direct Debit, Standard Credit, and Prepayment sensitivity runs. Fuel mapping is also scenario-specific: gas and electricity properties are eligible for the domestic S0--S4 and S6 tariff-cap spine, while the 502 oil-heated properties form a separate S5 heating-oil sensitivity group and should not be joined to gas or electricity cap scenarios.

The resulting dataset is therefore best understood as a property-level modelling backbone for current required-burden exposure and future scenario analysis. It is not a direct observation of each household's income, consumption, or current tenure contract. This boundary is important: the modelling design is intended to reveal which property--income--governance combinations are likely to be exposed, not to certify household-level fuel-poverty status.
