\section{Expected Outputs}

The empirical outputs are designed to move from an implemented income--cost baseline to forward-looking price-risk and intervention comparisons. The latest verified modelling round already provides the first layer of this sequence: a property-level baseline required-energy-burden engine for Westminster, built from constrained LSOA income distributions and SAP-derived required energy costs. The run labelled \texttt{20260520\_213323} covers 124,980 EPC property records across 126 LSOAs and 26 MSOAs. It preserves MSOA after-housing-cost income consistency while allowing LSOA differentiation mainly through income dispersion and lower-tail probability, rather than by claiming directly observed household incomes.

\subsection{Implemented Baseline Outputs}

The current outputs support three baseline products. First, the model estimates LSOA lognormal income parameters, including $\mu_l$, $\sigma_l$, lower-tail probabilities below \pounds 19{,}009, and the selected MSOA-level regularisation parameter $\lambda$. In the latest verified run, the ratio of LSOA mean income to MSOA income is tightly anchored, ranging from 0.999650 to 1.000309, while $\sigma_l$ ranges from 0.4192 to 1.4000. Only 3 of 126 LSOAs sit at the new upper bound, compared with 31 of 126 under the previous bound of 0.9. This indicates that within-MSOA differentiation is being carried primarily by dispersion and tail probability.

Second, the model produces property-level SAP-derived required energy cost and the probability that required energy burden exceeds a 10 percent threshold. This output should be interpreted as baseline required-energy affordability exposure, not as a complete household fuel price risk measure. It provides the denominator and cost foundation for later shock scenarios, while avoiding dependence on actual expenditure that may be suppressed by underheating or self-rationing.

Third, the baseline module generates a modelled LSOA fuel-poverty comparison used for calibration diagnostics. The latest run has a mean modelled-minus-official LSOA fuel-poverty-rate error of -0.0174, a median error of -0.0270, and a worst absolute error of 0.133. This residual gap is substantively useful rather than merely technical: it shows that income-tail matching alone does not reproduce official fuel-poverty geography, reinforcing the paper's distinction between income deprivation, required energy burden, dwelling fabric, heating systems, tenure, and future price risk.

\subsection{Implemented High-Risk Explanation Outputs}

The latest high-risk explanation stage adds an audited EPC-enriched stock and a descriptive pathway typology. The enriched master retains 124,980 Westminster property records. After corrected UPRN standardisation, the QA workbook reports a complete match between the master properties and EPC certificate records, with zero unmatched master rows. The corrected EPC tenure proxy distributes the stock into 58,744 private rented properties, 43,686 owner-occupied properties, 20,066 social rented properties, and 2,484 unknown-tenure properties. These tenure categories are analytical proxies and should be interpreted as adaptive-capacity and governance indicators rather than as verified household tenure records.

The implemented high-risk groups remain exploratory and model-based. HR10 contains the 12,500 properties in the top decile of the probability that required energy burden exceeds 10 percent; HR20 contains the 24,996 properties in the top quintile. The deterministic burden robustness groups contain 12,498 BR10 properties and 24,996 BR20 properties, while only 737 properties have a baseline required energy burden above 10 percent under the deterministic baseline measure. HR10 and BR10 overlap for 7,128 properties, or 57.0 percent of each group. This overlap is large enough to show that the probabilistic and deterministic indicators identify a related high-burden tail, but incomplete enough to justify reporting both.

The strongest descriptive signal in the current outputs is the interaction between dwelling size and energy performance. EPC E--F--G properties above 120 m$^2$ have an HR10 share of 69.68 percent and an HR20 share of 85.21 percent, with a median baseline burden of 7.26 percent. E--F--G houses also show high within-type exposure, with an HR10 share of 56.08 percent. By contrast, E--F--G flats have a lower within-type HR10 share of 19.38 percent, but remain important because flats are numerous in the Westminster stock.

\begin{table}[htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{3pt}
\caption{Current high-risk pathway typology from the latest explanatory run}
\label{tab:high-risk-pathways}
\begin{tabular}{p{0.36\linewidth}rrrr}
\toprule
Pathway & Properties & Stock & HR10 & HR10 contrib. \\
\midrule
Inefficient large owner-occupied gas houses & 2,802 & 2.24\% & 50.25\% & 11.26\% \\
Social rented estate/block risk & 7,016 & 5.61\% & 22.66\% & 12.72\% \\
Private rented weak-fabric gas flats & 34,672 & 27.74\% & 4.18\% & 11.60\% \\
Electric-heated inefficient flats/maisonettes & 10,256 & 8.21\% & 13.83\% & 11.34\% \\
High-demand inefficient maisonettes & 2,220 & 1.78\% & 25.81\% & 4.58\% \\
Other high-risk residual group & 13,063 & 10.45\% & 46.40\% & 48.49\% \\
Not high risk / comparison stock & 54,951 & 43.97\% & 0.00\% & 0.00\% \\
\bottomrule
\end{tabular}
\end{table}

The pathway table should be read as a targeting and interpretation device, not as a final causal attribution model. It separates two policy-relevant rankings: the highest within-pathway risk is concentrated in inefficient large owner-occupied gas houses, high-demand inefficient maisonettes, and social rented estate/block risk, while the largest contributions to all HR10 properties come from social rented estate/block risk, private rented weak-fabric gas flats, electric-heated inefficient flats/maisonettes, and the residual high-risk group. The next empirical outputs should therefore report both risk intensity and stock-scale contribution.

\subsection{Risk and Intervention Outputs}

The next empirical layer will convert the baseline engine into price-shock outputs. These will include LSOA/MSOA maps, property-archetype summaries, distributional plots, and threshold-crossing estimates under gas-price, electricity-price, combined-fuel, standing-charge, and policy-mitigation scenarios. The paper will report not only average burden changes, but also upper-tail risk, burden uplift, and the probability that households cross policy-relevant burden thresholds.

A central output is the de-risking dividend:
\begin{equation}
\text{De-risking dividend} = \text{Fuel Price-at-Risk}_{\text{before}} - \text{Fuel Price-at-Risk}_{\text{after}}.
\end{equation}
This metric will be estimated by intervention package and household-dwelling condition, including fabric retrofit, clean heat, PV, battery storage, smart tariffs, and integrated packages. Its interpretation will remain conditional: an intervention produces household price-risk protection only where technical feasibility, tenure and leasehold governance, tariff access, electricity/gas price ratios, and market pass-through allow the engineering change to reduce household exposure.

\subsection{Figures and Tables}

Expected tables will summarise baseline burden probabilities, modelled fuel-poverty diagnostics, price-shock burden uplift, Fuel Price-at-Risk, and intervention-specific de-risking dividends by income group, EPC rating, dwelling form, heating system, tenure, and LSOA/MSOA. Expected figures will include: the conceptual distinction between fuel poverty, energy burden, and household fuel price risk; maps of baseline required-energy-burden exposure; distributional plots of shock-induced burden uplift; intervention de-risking comparisons; and maps of de-risking gaps.

The latest high-risk explanation stage also identifies near-term manuscript figures: a side-by-side comparison of HR10 share within each pathway and each pathway's contribution to all HR10 properties; an EPC-band by floor-area heatmap coloured by HR10 share; a tenure-proxy by EPC-band heatmap; an LSOA map of HR10 share; an LSOA map of the dominant HR10 pathway; and, if needed, an alluvial chart linking tenure, property type, EPC band, and pathway. These should be promoted to \texttt{paper/figures/} only after specific figure files are selected and checked.

The synced LSOA income PDF panels from the latest run are useful writing and diagnostic references. They show the estimated lognormal income distributions under selected $\lambda$ values, with poverty-line and MSOA-mean markers. If promoted into the manuscript, they should be captioned as synthetic constrained income distributions for burden modelling, not as observed household income distributions and not as direct household fuel price risk outputs.

The paper will ultimately identify de-risking gaps: places and household-dwelling types where fuel price protection is most needed but low-carbon intervention is least accessible. These gaps are expected to be especially important where Westminster's high housing costs, private renting, leasehold flats, heritage constraints, district-heating governance, and uneven tariff or asset access interrupt the translation from domestic net zero investment into household price-risk protection.
