\section{Discussion}

The expected policy implication is that domestic net zero should be treated as a distributional household risk-protection agenda. Protection depends on the alignment of fabric retrofit, heating technology, distributed generation, flexibility, tariff design, electricity market reform, capital access, and tenure-sensitive governance.

In Westminster, this means paying particular attention to private renters, leasehold flats, HMOs, heritage-constrained dwellings, district-heating governance, social housing delivery pathways, and households whose vulnerability is masked by high neighbourhood average wealth.

The latest high-risk explanatory results sharpen this argument. Westminster's current modelled high-burden tail is not produced by a single deficit such as low EPC performance alone. It emerges through multiple routes: high required heat demand, weak fabric, income sensitivity, tenure governance, electricity price exposure, and limited household control over building-level interventions. This matters because the policy question is not simply where average bills are high, but where future price shocks are likely to meet constrained adaptive capacity.

The income-distribution sensitivity results add a methodological caution to this interpretation. The pseudo-Huber L1 lower-tail constraint and alternative MSOA income anchors do not remove the residual gap between the modelled poverty proxy and official LSOA fuel-poverty rates. That persistence should not be treated as a failed calibration exercise. It shows that income deprivation, required-energy burden, and official fuel poverty are related but non-identical constructs. The paper's price-risk analysis should therefore build on the baseline income--cost layer while continuing to reserve household fuel price risk for explicit price-shock and intervention scenarios.

The baseline extract figures sharpen the same point. Figure~\ref{fig:baseline-burden-distribution} shows that very few properties cross a 10 percent burden threshold under an MSOA point-income denominator, whereas Figure~\ref{fig:burden-prob-distribution} shows a broader probability tail once LSOA income distributions are introduced. This contrast is not a technical nuisance; it is central to the paper's argument. Westminster's exposure is partly hidden by aggregate income measures, so the model must retain both deterministic burden intensity and distributional threshold probability before moving to future price shocks.

The new baseline-cost sensitivity results add a second caution. Figure~\ref{fig:sap-epc-cost-scatter} shows that SAP-inverse total cost and EPC heating, hot water, and lighting component cost identify overlapping but far from identical high-burden tails. This matters because the first step in a household fuel price risk model is not only the choice of shock scenario; it is the translation from dwelling data into the baseline required-cost numerator. Figure~\ref{fig:standing-burden-uplift-property-type} then shows that standing charges modestly raise burden levels without strongly reordering the highest-burden group under the present reconstruction. The policy implication is precise: standing charges should remain explicit in the price-shock engine, but this exploratory run does not justify claiming that standing charges alone rerank Westminster property types into the highest-risk tail.

The property-type and fuel-composition figures add a third baseline caution. Figure~\ref{fig:baseline-high-burden-property-type} shows that flats are numerous, but houses and maisonettes are disproportionately represented in the current high-burden groups. Figure~\ref{fig:baseline-high-burden-main-fuel} shows that electricity exposure is a minority condition, yet slightly more common in the HR groups than in the stock as a whole. These patterns reinforce the paper's conditional interpretation of domestic net zero: the relevant question is not whether a property is a flat, a house, gas-heated, or electric-heated in isolation, but how dwelling form, required demand, income-tail sensitivity, fuel prices, and governance constraints combine.

The official price-spine materials sharpen the third caution: price shocks are not interchangeable. Figures~\ref{fig:official-price-spine-timeline}--\ref{fig:official-price-spine-s6} show that unmitigated cap exposure, EPG-mitigated unit rates, off-gas heating-oil exposure, and standing-charge reallocation enter the household risk model through different mechanisms. The S3/S4 contrast is especially important because it separates market exposure from policy buffering rather than treating observed 2022Q4 bills as a simple price increase. S6 is equally important for interpretation because it tests fixed-cost exposure under a tariff-structure change, while retaining the documented proxy caveat for Q3 values. The policy implication is that protection cannot be inferred from a lower average unit rate alone; it must be tested against unit-rate exposure, standing-charge exposure, payment method, required demand, and household adaptive capacity.

The first price-shock results turn this caution into an empirical distribution. Figure~\ref{fig:shock-mechanism-heatmaps} shows that S3 exposure is structurally produced by fuel, fabric, and dwelling form: gas-heated E--G dwellings and E--G houses experience much larger burden uplifts than efficient electric dwellings or flats. Figure~\ref{fig:shock-top-archetypes} then shows that the highest-risk groups are specific household-dwelling archetypes, not a generic low-income category. This matters because burden uplift and threshold-crossing probability are related but not identical. Some groups have large price-sensitive cost increases because of dwelling and fuel structure, while others have high threshold risk because income-tail sensitivity leaves little capacity to absorb even smaller increases.

The scenario and spatial results add two further implications. Figure~\ref{fig:shock-scenario-profiles} indicates that EPG-style policy mitigation reduces threshold-crossing risk but leaves a strong residual gradient by EPC band, fuel, and tenure. It therefore supports a conditional view of public protection: mitigation dampens the shock, but it does not erase the housing and income mechanisms that produce exposure. Figure~\ref{fig:shock-spatial-distribution} shows that this residual exposure is geographically concentrated inside Westminster. The borough's contribution is therefore not merely that it contains high-risk properties, but that local housing stock, tenure composition, and income distributions translate national tariff shocks into uneven neighbourhood-level risk.

The formal risk metric layer strengthens this interpretation by moving from scenario-by-scenario shock results to upper-tail household risk indicators. Figure~\ref{fig:risk-metric-fpar-spatial} shows that mean \texttt{FPaR\_P90} is spatially uneven across Westminster, while Figure~\ref{fig:risk-metric-archetypes} shows that the highest tail-risk archetypes are concentrated among gas-heated houses and maisonettes with weak EPC performance. These results make the paper's concept operational: household fuel price risk is not simply the largest S3 uplift, nor the current baseline burden, but the upper-tail burden that persists across a defined set of shock and tariff-structure scenarios.

Figure~\ref{fig:risk-metric-policy-residual} is especially important for policy interpretation. The S4 comparison shows that public mitigation reduces exposure but leaves around three quarters of S3 burden among the highest-risk archetypes in this layer. This does not mean that policy support is ineffective. It means that policy buffering and structural de-risking are different objects. Bill support can reduce immediate severity, while fabric, fuel, tariff access, and governance still determine who remains exposed when the next shock arrives.

The interaction between dwelling size and EPC performance is especially important (Figure~\ref{fig:epc-floorarea-hr10}). Inefficient large dwellings have the highest within-type modelled burden probability, showing that poor fabric becomes most consequential where required energy demand is high. Yet the pathway typology also shows that intensity and scale are different policy problems (Figure~\ref{fig:high-risk-pathway-contribution}). Inefficient large owner-occupied gas houses are a small but high-intensity group, while private rented weak-fabric gas flats and electric-heated inefficient flats or maisonettes contribute materially to the high-risk tail because they are common in the stock. A targeting strategy based only on the highest within-group risk would miss large numbers of exposed households; a strategy based only on stock counts would miss the households facing the steepest required-burden pressure.

Tenure changes the route through which de-risking can occur (Figure~\ref{fig:tenure-by-pathway}). Owner occupation does not automatically imply adaptive capacity where heritage rules, planning constraints, capital cost, and disruption limit retrofit. Social rented estate and block risk is primarily a delivery and governance problem: tenants cannot individually decide the timing, specification, or financing of estate-level fabric works, heating-system changes, or metering reform. Private rented weak-fabric flats raise a different problem of split incentives, enforcement, and minimum-standard compliance, especially where moderate aggregate EPC ratings obscure component-level fabric weakness.

The electric-heating pathway reinforces the paper's caution about electrification (Figure~\ref{fig:electric-exposure}). Electric-heated inefficient flats and maisonettes may already be exposed to high electricity unit costs. Unless fabric improvement, tariff reform, flexibility access, and electricity-market design reduce the household-facing price exposure, electrification can reduce emissions before it reduces household fuel price risk. The empirical strategy should therefore test clean heat, PV, batteries, smart tariffs, and integrated packages under explicit gas-to-electricity price-ratio assumptions rather than treating electrification as automatic protection.

The residual pathway is also substantively important. Nearly half of HR10 properties sit in the residual high-risk group, indicating that income sensitivity, local deprivation, and mixed mechanisms remain central to the current burden-risk distribution. The next modelling stage should therefore separate housing-driven, income-driven, and mixed-mechanism risk before estimating intervention de-risking dividends. This is not a weakness of the typology; it is evidence that the paper should avoid reducing household fuel price risk to a single housing-technology variable.

The broader implication is that domestic net zero policy must be evaluated against pathway-specific routes to protection. Fabric-first retrofit is most directly relevant where high required heat demand and poor energy performance dominate. Social housing pathways require block-level delivery, tenant protection, and post-intervention bill assessment. Private rented pathways require enforcement, landlord incentives, and tenant safeguards. Electric-heating pathways require tariff and flexibility reform as much as technology substitution. Off-gas pathways require attention to unregulated fuel exposure rather than Ofgem cap logic. Residual income-driven pathways may need social tariffs, standing-charge reform, or income support before household risk can be materially reduced. The empirical test of domestic net zero is therefore not whether interventions look effective on average, but whether they reach the mechanisms through which exposure is produced.
