\section{Conclusion}

Fuel poverty identifies current hardship; household fuel price risk identifies future exposure to price shocks. Net zero determines who receives protection only when domestic interventions are technically effective, financially accessible, and institutionally deliverable for the households most exposed.

The current Westminster evidence strengthens this framing. Modelled high-burden exposure is heterogeneous: large inefficient gas houses, social rented blocks, private rented weak-fabric flats, electric-heated inefficient flats and maisonettes, high-demand maisonettes, and residual income-sensitive cases represent different routes into risk and different routes out of it. The latest sensitivity evidence also shows that baseline required-cost definition and price-structure representation shape which households appear most exposed before any future shock is modelled. A single technology narrative or a single total-cost scalar cannot explain this distribution.

The 2026-05-28 baseline extract makes this empirical sequence clearer. It provides a fixed property-level input layer with SAP-inverse required cost as the main baseline metric, EPC component cost as the price-revaluable bridge, payment method as a sensitivity dimension, and fuel-specific scenario coverage. Its figures show why point burden, distributional burden probability, property type, and fuel exposure must be read together before household fuel price risk is estimated.

The official price-spine materials now make the next step more precise. Future risk can be estimated against a documented S0--S6 scenario architecture that separates pre-shock reference prices, post-COVID and Ukraine-era unit-rate shocks, EPG policy buffering, heating-oil exposure, and fixed standing-charge sensitivity. This strengthens the paper's central distinction: price evidence is an input to risk modelling, not the risk outcome itself.

The first price-shock result figures move the manuscript from this input architecture into an initial risk distribution. They show that S3 exposure is amplified by gas heating, weak fabric, and dwelling form; that the most exposed Westminster groups are specific tenure--dwelling--EPC--fuel archetypes; that S4 policy mitigation reduces but does not remove threshold-crossing risk; and that S3 risk is spatially concentrated within the borough. These findings strengthen the paper's central claim that household fuel price risk is a forward-looking distributional relation, not simply a synonym for current fuel poverty or average energy bills.

The paper therefore asks not whether net zero reduces emissions, but whether, how, and for whom it credibly reduces household exposure to fossil-fuel price volatility. Its policy implication is correspondingly conditional: domestic net zero becomes household protection only where fabric, heating systems, tariffs, market design, finance, tenure, and local governance convert technical change into reduced upper-tail burden risk.
